\Wxxsir methods to estimate $\rr$ in the SIR model with applications to 2009 pandemic influenza

### 2018-09-04 paper/Version16/draft_v16.tex
Added changes to version 16

We implement the \wxxsir methods to estimate $\rr$ using the baseline data set with normal error.  The results are displayed in Figure \ref{fig:baseline-res} and Table \ref{tab:baseline-res}.
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.5]{images/BaseBase.jpeg}
  \caption{Forest plots of estimates of $\rr$ for the \xxsir methods for the baseline data set $(\beta=.06, \gamma=.03, O=365, X(0)=99950, Y(0)=50, Z(0)=0, \sigma_X=100, \sigma_Y=5, N=10^5)$.  The points are the estimates of $\rr$ and the lines denote $\pm 2\cdot $Std. Err.  The vertical, dashed line is the true $\rr$ value.}\label{fig:baseline-res}
  \end{figure}

\begin{table}[H]	
	\centering
	\begin{tabular}[t]{l|r|r}
		\hline
		Model & Estimate & Std. Err\\
		\hline
		RE & 1.9999711 & 0.0056\\
		\hline
		rRE & 1.9997340 & 0.0050\\
		\hline
		LMA & 1.6863640 & 0.1886\\
		\hline
		LMAT & 1.4063227 & 0.6309\\
		\hline
		IPR & 4.4203632 & 12.3593\\
		\hline
		SIPR & 1.8870824 & $<$ 1e-04 \\
		\hline
		LL & 1.9998072 & 0.0002\\
		\hline
		MC & 0.9485555 &  $<$ 1e-04 \\
		\hline
		SB & 1.6495023 & 0.0672\\
		\hline
	\end{tabular}
        \caption{Baseline Data $(\beta=.06, \gamma=.03, T=365, X(0)=99950, Y(0)=50, Z(0)=0, \sigma_X=100, \sigma_Y=5, N=10^5)$, $\rr$ Estimates and Standard Errors}\label{tab:baseline-res}
\end{table}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.5]{images/start_arm.jpeg}
	\caption{Forest plots of estimates of $\rr$ for the \xxsir methods for the Inits1-4 data sets $(\beta=.06, \gamma=.03, T=365,  Z(0)=0, \sigma_X=100, \sigma_Y=5, N=10^5)$.  The points are the estimates of $\rr$ and the lines denote $\pm 2\cdot $Std. Err.  The vertical line is the true $\rr$ value.}\label{fig:ar-small-I}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.5]{images/parchange_ar.jpeg}
	\caption{Forest plots of estimates of $\rr$ for the \xxsir methods for the infrec1-4 data sets $(T=365, X(0)=99950, Y(0)=50, Z(0)=0, \sigma_X=100, \sigma_Y=5, N=10^5)$.  The points are the estimates of $\rr$ and the lines denote $\pm 2\cdot $Std. Err.  The vertical line is the true $\rr$ value.}\label{fig:ar-r0}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.5]{images/timediff.jpeg}
	\caption{Forest plots of estimates of $\rr$ for the \xxsir methods for the baseline data sets with normall error structure $(\beta=.06, \gamma=.03, X(0) = 99950, Y(0)=50, \sigma_X=100, \sigma_Y=5, N=10^5)$.  The points are the estimates of $\rr$ and the lines denote $\pm 2\cdot $Std. Err.  The vertical line is the true $\rr$ value.}\label{fig:timediff}
      \end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.5]{images/obs.jpeg}
	\caption{Forest plots of estimates of $\rr$ for the \xxsir methods for the baseline data sets with normall error structure $(\beta=.06, \gamma=.03, X(0) = 99950, Y(0)=50, \sigma_X=100, \sigma_Y=5, N=10^5)$.  The points are the estimates of $\rr$ and the lines denote $\pm 2\cdot $Std. Err.  The vertical line is the true $\rr$ value.}\label{fig:obs}
\end{figure}

@@

	\centering
	\begin{tabular}[t]{l|r|r|r|r}
		\hline
		Model & Mean Estimate & Std. Dev. & Baseline Estimate & Baseline SE\\
		\hline
		RE & 2.0000 & 0.0003 & 1.9999 & 0.0058\\
		\hline
		rRE & 2.0000 & 0.0003 & 1.9997 & 0.0052\\
		\hline
		LMA & 1.8497 & 0.3339 & 1.9974 & 0.3900\\
		\hline
		LMAT & 1.4562 & 0.3577 & 1.3980 & 0.6028 \\
		\hline
		IPR & 4.5214 & 0.3705 & 2.5930 & 9.0408\\
		\hline
		SIPR & 1.7973 & 0.0951 & 0.9251 & $<$ 1e-04 \\
		\hline
		LL & 2.0000 & 0.0003 & 1.9998 & 0.0002\\
		\hline
		MC & 0.9486 & $<$ 1e-04 & 0.9486 & $<$ 1e-04\\
		\hline
		SB & 1.1330 & 0.4163 & 1.0000 & 0.0523\\
		\hline
	\end{tabular}
        \caption{Mean $\rr$ Estimates and Std. Devs, Delta Method/Posterior}
        \label{tab:rep-samp}
\end{table}

@@

	\centering
	\begin{tabular}[t]{l|r|r|r|r}
		\hline
		Model & Mean Estimate & Std. Dev. & Baseline Estimate & Baseline SE\\
		\hline
		RE & 1.9999 & 0.0003 & 1.9999 & 0.0058\\
		\hline
		rRE & 1.9998 & 0.0003 & 1.9997 & 0.0052\\
		\hline
		LMA & -0.9975 & 21.7161 & 1.9974 & 0.3900\\
		\hline
		LMAT & 1.5138 & 1.0485 & 1.3980 & 0.6028 \\
		\hline
		SIPR & 0.7762 & 2.6624 & 0.9252 & $<$ 1e-04 \\
		\hline
	\end{tabular}
	\caption{Mean $\rr$ Estimates and Std. Devs, Block Bootstrap}
	\label{tab:bb-samp}
\end{table}

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[scale=0.5]{images/coverage2.jpeg}
		\caption{Proportion of coverage of true $\rr$ of confidence intervals produced by repeated sampling for the applicable method (delta method or posterior).}
		\label{fig:coverage}	
	\end{center}
\end{figure}

\begin{figure}[H]
	\begin{center}
		\includegraphics[scale=0.5]{images/coverage.jpeg}
		\caption{Proportion of coverage of true $\rr$ of confidence intervals produced by repeated sampling for block bootstrapping.}
		\label{fig:coverage}	
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{images/h1n1.jpeg}
	\caption{Results from SIR models on H1N1 data.}
\end{figure}

>>>>

We implement the \wxxsir methods to estimate $\rr$ using the baseline data set with normal error.  The results are displayed in Figure \ref{fig:baseline-res} and Table \ref{tab:baseline-res}.
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.5]{images/BaseBase.tiff}
  \caption{Forest plots of estimates of $\rr$ for the \xxsir methods for the baseline data set $(\beta=.06, \gamma=.03, O=365, X(0)=99950, Y(0)=50, Z(0)=0, \sigma_X=100, \sigma_Y=5, N=10^5)$.  The points are the estimates of $\rr$ and the lines denote $\pm 2\cdot $Std. Err.  The vertical, dashed line is the true $\rr$ value.}\label{fig:baseline-res}
  \end{figure}

\begin{table}[H]	
	\centering
	\begin{tabular}[t]{l|r|r}
		\hline
		Model & Estimate & Std. Err\\
		\hline
		RE & 2.0000 & 0.0056\\
		\hline
		rRE & 1.9997 & 0.0050\\
		\hline
		LMA & 1.6864 & 0.1886\\
		\hline
		LMAT & 1.4063 & 0.6309\\
		\hline
		IPR & 4.4204 & 12.3593\\
		\hline
		SIPR & 1.8871 & $<$ 1e-04 \\
		\hline
		LL & 1.9998 & 0.0002\\
		\hline
		MC & 0.9486 &  $<$ 1e-04 \\
		\hline
		SB & 1.6495 & 0.0672\\
		\hline
		LBE & 14.6784 & 1.2330\\
		\hline
	\end{tabular}
        \caption{Baseline Data $(\beta=.06, \gamma=.03, T=365, X(0)=99950, Y(0)=50, Z(0)=0, \sigma_X=100, \sigma_Y=5, N=10^5)$, $\rr$ Estimates and Standard Errors}\label{tab:baseline-res}
\end{table}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.5]{images/start_arm.tiff}
	\caption{Forest plots of estimates of $\rr$ for the \xxsir methods for the Inits1-4 data sets $(\beta=.06, \gamma=.03, T=365,  Z(0)=0, \sigma_X=100, \sigma_Y=5, N=10^5)$.  The points are the estimates of $\rr$ and the lines denote $\pm 2\cdot $Std. Err.  The vertical line is the true $\rr$ value.}\label{fig:ar-small-I}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.5]{images/parchange_ar.tiff}
	\caption{Forest plots of estimates of $\rr$ for the \xxsir methods for the infrec1-4 data sets $(T=365, X(0)=99950, Y(0)=50, Z(0)=0, \sigma_X=100, \sigma_Y=5, N=10^5)$.  The points are the estimates of $\rr$ and the lines denote $\pm 2\cdot $Std. Err.  The vertical line is the true $\rr$ value.}\label{fig:ar-r0}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.5]{images/timediff.tiff}
	\caption{Forest plots of estimates of $\rr$ for the \xxsir methods for the baseline data sets with normal error structure $(\beta=.06, \gamma=.03, X(0) = 99950, Y(0)=50, \sigma_X=100, \sigma_Y=5, N=10^5)$.  The points are the estimates of $\rr$ and the lines denote $\pm 2\cdot $Std. Err.  The vertical line is the true $\rr$ value.}\label{fig:timediff}
      \end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.5]{images/obs.tiff}
	\caption{Forest plots of estimates of $\rr$ for the \xxsir methods for the baseline data sets with normal error structure $(\beta=.06, \gamma=.03, X(0) = 99950, Y(0)=50, \sigma_X=100, \sigma_Y=5, N=10^5)$.  The points are the estimates of $\rr$ and the lines denote $\pm 2\cdot $Std. Err.  The vertical line is the true $\rr$ value.}\label{fig:obs}
\end{figure}

@@

	\centering
	\begin{tabular}[t]{l|r|r|r|r}
		\hline
		Model & Mean Estimate & Std. Dev. & Baseline Estimate & Baseline SE\\
		\hline
		RE & 2.0000 & 0.0003 & 1.9999 & 0.0058\\
		\hline
		rRE & 2.0000 & 0.0003 & 1.9997 & 0.0052\\
		\hline
		LMA & 1.8497 & 0.3339 & 1.9974 & 0.3900\\
		\hline
		LMAT & 1.4562 & 0.3577 & 1.3980 & 0.6028 \\
		\hline
		IPR & 4.5214 & 0.3705 & 2.5930 & 9.0408\\
		\hline
		SIPR & 1.7973 & 0.0951 & 0.9251 & $<$ 1e-04 \\
		\hline
		LL & 2.0000 & 0.0003 & 1.9998 & 0.0002\\
		\hline
		MC & 0.9486 & $<$ 1e-04 & 0.9486 & $<$ 1e-04\\
		\hline
		SB & 1.1330 & 0.4163 & 1.0000 & 0.0523\\
		\hline
		LBE & 8.5926 & 6.9421 & 14.6784 & 1.2330\\
		\hline
	\end{tabular}
        \caption{Mean $\rr$ Estimates and Std. Devs, Delta Method/Posterior}
        \label{tab:rep-samp}
\end{table}

@@

	\centering
	\begin{tabular}[t]{l|r|r|r|r}
		\hline
		Model & Mean Estimate & Std. Dev. & Baseline Estimate & Baseline SE\\
		\hline
		RE & 1.9999 & 0.0003 & 1.9999 & 0.0058\\
		\hline
		rRE & 1.9998 & 0.0003 & 1.9997 & 0.0052\\
		\hline
		LMA & -0.9975 & 21.7161 & 1.9974 & 0.3900\\
		\hline
		LMAT & 1.5138 & 1.0485 & 1.3980 & 0.6028 \\
		\hline
		SIPR & 0.7762 & 2.6624 & 0.9252 & $<$ 1e-04 \\
		\hline
		LBE & 19.9935 & 10.640 & 14.6784 & 1.2330 \\
		\hline
	\end{tabular}
	\caption{Mean $\rr$ Estimates and Std. Devs, Block Bootstrap}
	\label{tab:bb-samp}
\end{table}

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[scale=0.5]{images/coverage2.tiff}
		\caption{Proportion of coverage of true $\rr$ of confidence intervals produced by repeated sampling for the applicable method (delta method or posterior).}
		\label{fig:coverage}	
	\end{center}
\end{figure}

\begin{figure}[H]
	\begin{center}
		\includegraphics[scale=0.5]{images/coverage.tiff}
		\caption{Proportion of coverage of true $\rr$ of confidence intervals produced by repeated sampling for block bootstrapping.}
		\label{fig:coverage}	
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{images/h1n1.tiff}
	\caption{Results from SIR models on H1N1 data.}
\end{figure}
